%Experience
\section{Work Experience}

\begin{minipage}{\textwidth}
  \large{\textbf{Peloton}} \\
  \textit{Site Reliability Engineer} \hfill Feb 2018 - May 2024 \\[3.75pt]
  \textit{IaC Subject Matter expert, building out a fully featured, internal IaC platform}
\end{minipage}

\begin{itemize}
  \item Architected internal Terraform/Terragrunt-powered IaC (Infrastructure as Code) platform for global company infrastructure. Servicing $\sim$3000 individually managed services. Allowing self-service module and service releases.
    \begin{itemize}
      \item[--] 10 core AWS accounts, 30 sandbox accounts
      \item[--] AWS, Cloudflare, and Datadog modules
      \item[--] GitOps for plan, apply, and rollback
      \item[--] Fully containerized environment
      \item[--] Automated, Datadog alerting and paging
    \end{itemize}
  \item Wrote Golang command line tools for Terraform manual operations, providing state backup, breakglass role escalation, and command shortcuts for operators
  \item Provided Vue.js web frontends to help visualize complexity of platform in human digestible form
  \item Lead 2 infrastructure migrations from Terraform 0.11 to 0.12 and again from 0.12 to 0.15
  \item Co-ordinated and lead support for devs and operators, provided consultation to onboard and raise competency with Terraform and platform. Provided 24/7 oncall support for platform, and managed company-wide drift detection. Trained and managed contracted support team. Planned and delegated feature and stability improvements to contractors.
  \item Designed automated Terragrunt dependency manager, to assist users in deploying the correct code every time, handling rollbacks, and tracking inter-team dependencies.
    \begin{itemize}
      \item[--] Allowed full Disaster Recovery story for recovering cloud infra
      \item[--] Guarded against teams unintentionally impacting each other
      \item[--] Tracked both module and service dependencies
    \end{itemize}
  \item Managed Chef cookbooks for legacy EC2 fleet. Maintained integration and unit tests, and handled node provisioning and decommission lifecycle.
  \item Administered Jenkins cluster. Provided isolated Jenkins instance for individual teams, and provided guidance on on-boarding new projects and tests into Jenkins cluster
\end{itemize}

\begin{minipage}{\textwidth}
  \large{\textbf{LiquidSky}} \\
  \textit{Site Reliability Engineer} \hfill June 2017 - Jan 2018 \\[3.75pt]
  \textit{SRE tasked with unifying and simplifying the sprawl of hand configured machines. Wrangling growth into sustainable platform}
\end{minipage}

\begin{itemize}
  \item Operated Docker service mesh, backed by Consul for internal tooling
  \item Organized company image library with Ansible and Packer tooling for AWS and IBM, providing consistent platform in hybrid cloud
  \item Managed and maintained ZFS storage backend vendor relationship
  \item Imported existing infrastructure into Terraform. Handled transition from Elastic Beanstalk to internal Docker platform
\end{itemize}

\begin{minipage}{\textwidth}
  \large{\textbf{Service Fusion}} \\
  \textit{Full Stack Developer} \hfill August 2016 - December 2016 \\[3.75pt]
  \textit{Full stack developer in charge of migrating SPA to new tech}
\end{minipage}

\begin{itemize}
  \item Designed new website features for Vue.js based SPA (Single Page Application), taking them fully from user stories tickets to released features.
    \begin{itemize}
      \item[--] Internal email client
      \item[--] Websocket-powered authenticated chat client for client to customer communication
    \end{itemize}
  \item Managed migration from Web2py to Falcon.
    \begin{itemize}
      \item Evangelized and implemented first unit and integration tests company-wide
      \item Rewrote ORM (Object Relational Mapping) integration
    \end{itemize}
  \item Built Ansible-powered Debian build system for building and testing production artifacts
  \item Built Ansible playbooks for managing and deploying repeatable production servers
\end{itemize}

\begin{minipage}{\textwidth}
  \large{\textbf{Dyn}} \\
  \textit{Associate Sustaining Engineer} \hfill July 2014 - February 2016 \\[3.75pt]
  \textit{Browncoat front-line engineer, providing tooling directly to support staff}
\end{minipage}

\begin{itemize}
  \item Triaged recurring customer-related issues that escalated above support capabilities.
  \item Fixed bugs, implemented QoL, and maintained various legacy projects. Extending their lifecycle, freeing the devs to work on their replacement systems.
  \item Maintained internal Django tooling platform, used by customer support to directly service customer calls and concerns
    \begin{itemize}
      \item Added new functionality in response to changing user needs
      \item Built instrumentation for visualizing system help in collaboration with NOC
    \end{itemize}
\end{itemize}
